Time stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics (SUPPORTING INFORMATION)

### 2015-05-29 paper.tex
atualizando para compartilhar

\begin{abstract}
In this study, we demonstrate a remarkably stable activity in interaction networks. The activity along time and topology evolution were investigated in four e-mail lists by considering window sizes from 50 to 10,000 messages, which were made to slide and generate snapshots of the network in a timeline. The activity of participants followed the expected scale-free behavior, thus allowing us to establish three classes of vertices by comparying with the Erd\"os-R\'enyi model, namely hubs, intermediary and peripheral vertices. The relative size of these three sectors did not vary with time and was essentially the same for all e-mail lists. Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and the remainder are peripheral vertices. The metrics that contribute most to the dispersion of participants in the topological measures space were centrality measurements (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient. A clear distinction could be made of networks with few, stable agents, which possess a large number of threads per message, from others with many agents exhibiting intermittent activity and lower number of threads per message. Also important was the observation that the activity along time, in terms of seconds, minutes, hours, days and months, is practically the same for all lists. These results are coherent with literature and were found also in the analysis of other networks from other emails lists and from Facebook and Twitter. Therefore, the properties observed may be general for human interaction networks, which has important implications in establishing a typology based on objective, quantitative criteria.
\end{abstract}

>>>>

\begin{abstract}
In this study, we demonstrate a remarkably stable activity in interaction networks. The activity along time and topology evolution were investigated in four e-mail lists by considering window sizes from 50 to 10,000 messages, which were made to slide and generate snapshots of the network in a timeline. The activity of participants followed the expected scale-free behavior, thus allowing us to establish three classes of vertices by comparying with the Erd\"os-R\'enyi model, namely hubs, intermediary and peripheral vertices. The relative size of these three sectors did not vary with time and was essentially the same for all e-mail lists. Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and the remainder are peripheral vertices. The metrics that contribute most to the dispersion of participants in the topological measures space were centrality measurements (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient. A clear distinction could be made of networks with few, stable agents, which possess a large number of threads per message, from others with many agents exhibiting intermittent activity and lower number of threads per message. Also important was the observation that the activity along time, in terms of seconds, minutes, hours, days and months, is practically the same for all lists. These results are coherent with literature and were found also in the analysis of other networks from other emails lists and from Facebook, Twitter and Participa.br. Therefore, the properties observed may be general for human interaction networks, which has important implications in establishing a typology based on objective, quantitative criteria.
\end{abstract}

### 2015-05-29 supportingInformation.tex
atualizando para compartilhar

\begin{table*}[!h]
	\caption{Percentage of agents in each Erd\"os sector in the friendship and interaction human networks of Table~\ref{tab:E}. The ratios found in email networks are preserved. I1 and I4 are outliers, to which a possible explanation is that they are better characterized as a superposition of networks, rather than one coherent network.}
\begin{center}
\begin{tabular}{| l | c | c | c |}\hline
	 & periphery & intermediary & hubs \\ \hline\hline
	\input{tables/tabSectorsExtra}
\hline
\end{tabular}
\end{center}
\label{tab:secE}
\end{table*}

>>>>

\begin{table*}[!h]
	\caption{Percentage of agents in each Erd\"os sector in the friendship and interaction human networks of Table~\ref{tab:E}. The ratios found in email networks are preserved. I1 and I4 are outliers, to which a possible explanation is that they are better characterized as a superposition of networks, rather than one coherent network. Degree was used for sectorializing criteria.}
\begin{center}
\begin{tabular}{| l | c | c | c |}\hline
	 & periphery & intermediary & hubs \\ \hline\hline
	\input{tables/tabSectorsExtra}
\hline
\end{tabular}
\end{center}
\label{tab:secE}
\end{table*}
